### 2014-04-16 doc/uist14/iteration3.tex
added fixed figure

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of a user's head. However, this absolute orientation cannot be directly used in any indoor environment as the user may change their location. However, as long as the targets are spread around the periphery, their relative orientation to each other is stable (see Figure~\ref{fig:third_principle}). This key observation inspires us to investigate a hybrid solution with IR and orientation sensors on Glass.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_technique.pdf}
\caption{\ben{figure in interactionModel2.key file.} Our third technique learned each target's absolute orientation and construct the orientation map. Though we store the absolute orientation value, during the {\em refinement} stage, the prediction is only based on relative changes to a reference point. In such a way, the prediction will work regardless of user's position.}
\label{fig:third_technique}
\end{figure}

There are two phases to this technique: learning the relative orientations or targets in a room and intelligently suggesting targets during refinement.

>>>>

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of a user's head. However, this absolute orientation cannot be directly used in any indoor environment as the user may change their location. However, as long as the targets are spread around the periphery, their relative orientation to each other is relatively stable (see Figure~\ref{fig:third_principle}). This key observation inspires us to investigate a hybrid solution with IR and orientation sensors on Glass.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_technique3.pdf}
\caption{\ben{figure in interactionModel2.key file.} Our third technique learned each target's absolute orientation and construct the orientation map. Though we store the absolute orientation value, during the {\em refinement} stage, the prediction is only based on relative changes to a reference point. In such a way, the prediction will work regardless of user's position.}
\label{fig:third_technique}
\end{figure}

There are two phases to this technique: learning the relative orientations or targets in a room and intelligently suggesting targets during refinement (see Figure~\ref{fig:third_technique}).
